\section*{Acknowledgments}
I would like to thank the members of the \diiid\space PCI group.
My advisor, Professor Miklos Porkolab,
never lost faith in my ability to complete this project, and
he exercised patience as I developed into an independent scientist.
Chris Rost, my day-to-day supervisor,
spent countless hours with me in the \diiid\space ``pit'',
taught me the importance of being thorough and precise, and
brilliantly identified the origin of the noise crippling our system,
without which I may not have completed this project.
Alessandro Marinoni spent nearly as many hours working with me in the pit, and
he also ran the TGLF simulations
that tie nicely into the multiscale turbulence measurements
described in this thesis.

I would also like thank numerous other people from MIT.
In particular, Earl Marmar and John Belcher
served on my committee and slogged through
this tome of a thesis.
Earl also generously supported the last $3.5$ years of my studies
through the PSFC's MFE collaboration funds.
Conversations with Jim Irby were enlightening and
helped diagnose the enormous noise in our system.
Jessica Coco happily arranged much of my graduate travel,
substantially reducing the stress and bureaucracy of reimbursement.
Carol Arlington kept Miklos's exceptionally busy schedule organized,
ensuring he always had sufficient time to meet with me.
Jerry Hughes stood up for me when no one else would.
The graduate students of the PSFC were an enormous support network
during my first three years of graduate school;
of particular note are
Ian Faust,
Mark Chilenski (my officemate, who taught me a ton),
John Walk,
Choongki Sung (who subsequently became my \diiid\space control-room confidant),
and Ted Golfinopoulos.
Naoto Tsujii and Paul Ennever introduced me to the C-Mod PCI system.
The closure of C-Mod brought some dark times, but,
like a phoenix rising from the ashes,
I see a bright future for the PSFC, and
I am excited to see where everyone takes it.

I would additionally like to thank several people at \diiid,
where I spent the last $4.5$ years of my graduate studies.
Mike Van Zeeland and Tom Carlstrom,
the local interferometer gurus,
were always happy to share their extensive knowledge
of interferometry with me.
Daniel Finkenthal similarly shared his RF expertise and
provided \emph{pro bono} an automatic gain control amplifier, which
is crucial to the operation of our interferometer.
On several occasions, David Pace lent us channels
on his high-frequency $200$ MSPS digitizer, which
ultimately allowed Chris Rost to identify
the origin of the noise crippling our system.
R\'{e}jean Boivin checked in with me often
to ensure I was not ``falling between the cracks''.
Bob Pinsker fostered a collegiate atmosphere,
regularly hosting \diiid's student/postdoc seminar series, and
he also lent us the high-power RF amplifier needed to drive our AOM.
Lupe Cerda was always happy to help me navigate the \diiid\space bureaucracy.
The \diiid\space ``lunch crew'',
consisting of a hodge podge of graduate students, postdocs, and scientists
from multiple institutions,
always made for an entertaining lunch;
of particular note are
Matthias Kn{\"o}lker,
Mitchell Clement,
``Staff'' Tyler Abrams,
Ryan Sweeney,
Brent Covele, and
Wilkie Choi.
The short-lived ``Monday runday'' group
helped re-ignite my passion for running and
introduced me to running along the picturesque bluffs of La Jolla.

The Stewardship Science Graduate Fellowship (SSGF) program
generously supported the first $4$ years of my graduate study.
The Krell Institute, which administered the SSGF program, and
Lucille Kilmer in particular
were always a pleasure to interact with.

From Riverside, to Boston, to San Diego,
I have been blessed with some truly amazing friends.
John Paul Issa, you were there at the beginning, and
you were there at the end;
I feel like we have both been to our own personal hell and back, and
I am confident that the future is now bright.
You have always told it to me straight, but
you have never left me feeling bad.
Riley and Julia Takano, you make being responsible adults look so easy;
even a few hours with both of you has been enough to cure the lab blues.
Steven Warneke, it has been a long time
since our ``Titans of Industry'' talk and
our paths have swerved a bit since then, but
our friendship has only grown;
Madeline, I am so happy you found him and
are (mostly) keeping him out of trouble.
Rachel Cheong, you know me better than most and
still accept me for who I am;
you are beautiful inside and out.
Ian Faust, you made $881$ Mass Ave home, and
you truly helped me come into my own.
From Coachella to Oktoberfest,
you have never said no to adventure;
``unfortunately'', this has currently led you to Munich, but
even this has not put a wedge between us.
Alex Guo, you lead by example, and
you have a heart of gold.
Jason Ramapuram and Barbara Sandoval,
the kindness and friendship you both showed me
when I moved to San Diego
far exceeded my expectations;
your around-the-world adventures amaze and inspire me, but
I selfishly still wish you were in San Diego.
Matthias Kn{\"o}lker, from our off-hand introduction at lab
to where we are now, who could have guessed?
The only things that surprise me
more than your intuition and your humor
are your friendship and your loyalty.
Theresa Wilks, your optimism is infections, and
your laughter can move mountains.
Darren Burton \& co. (i.e.\ Scott and Andrew),
thanks for so many good times, good food, and
laughter inducing situations over the last year.

Finally, my family has always been the cornerstone of my life.
Cory, you've grown from being
my little brother to one of my best friends.
Your passions for astronomy and space exploration
have helped me remember why I got into science in the first place.
Thanks for never letting me forget where I came from.
Mom and Dad, you have been my number one fans since day one.
When I celebrated, you celebrated, and when I cried, you cried.
At this point, you are probably almost as well-versed in this thesis as I am.
Thank you for all of your love, support, and encouragement.
This thesis is dedicated to both of you.

This work was supported by
the U.S. Department of Energy,
Office of Science,
Office of Fusion Energy Sciences
under Award Numbers
DE-FG$02$-$94$ER$54235$,
DE-FC$02$-$04$ER$54698$, and
DE-FC$02$-$99$ER$54512$ and
the U.S. Department of Energy,
National Nuclear Security Administration,
Stewardship Science Graduate Fellowship program,
which is provided under grant number DENA$002135$.
